Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-29 draft.tex
fix typos

Confronted with this problem, a small but growing number of journals and
publishers have reacted by adopting explicit policies for data and software, for example the PLOS instructions on
\href{http://journals.plos.org/plosone/s/materials-and-software-sharing}{Materials
  and Software Sharing} and
on \href{http://journals.plos.org/plosone/s/data-availability}{Data Availability},
and the
\href{https://elifesciences.org/elife-news/inside-elife-forking-software-used-elife-papers-github}{recent
  annoucement} by eLife on forking (creating a linked copy of) software used in eLife papers to GitHub.
Such policies help to ensure access to code and data in a well-defined format
\citep{perkel:2016} but this will not guarantee reproducilbility nor
correctness.
At the educational and methodological levels, things have started to change with a
growing literature on best practices for making computations reproducible
\citep{sandve:2013, crook:2013, wilson:2014, halchenko:2015, janz:2015,
  hinsen:2015}.
  Related initiatives such as Software and Data Carpentry
\citep{wilson:2016} are of note since their goal is {\em to make
scientists more productive, and their work more reliable, by teaching them basic computing skills}.
Such best practices could be applied to already published research codebases as well, provided the original authors are willing to take on the challenge of 
re-implementing their software for the sake of better science.
Unfortunately, this is unlikely since the
incentives for doing such time-consuming work are low or nonexistent.
Furthermore, if the original authors made mistakes in their original
implementation, chances are that they will reproduce their mistakes.\\
% (just an educated guess, we have no data supporting this assertion)
%% At this point, the question is what do we do? Do we have to declare
%% the research to be lost once and for all because the associated software or
%% code is nowhere to be found / lost / damaged / malfunctioning / not runnable /
%% not usable / does not give original results / etc. We would doom ourselves by
%% doing so

@@

The possibility to imploy participants beyond the traditional group of
authors, editors, and reviewers is particularly interesting in the
case of ReScience, because it can be helpful to solicit input from the
authors of the original study that is being replicated. For example,
in one recent case
(\href{https://github.com/ReScience/ReScience-submission/pull/28}{\#28}),
a reviewer suggested asking the author of the original work for a
permission to re-use an image. The author intervened in the review and
granted permission.

>>>>

Confronted with this problem, a small but growing number of journals and
publishers have reacted by adopting explicit policies for data and software, for example the PLOS instructions on
\href{http://journals.plos.org/plosone/s/materials-and-software-sharing}{Materials
  and Software Sharing} and
on \href{http://journals.plos.org/plosone/s/data-availability}{Data Availability},
and the
\href{https://elifesciences.org/elife-news/inside-elife-forking-software-used-elife-papers-github}{recent
  annoucement} by eLife on forking (creating a linked copy of) software used in eLife papers to GitHub.
Such policies help to ensure access to code and data in a well-defined format
\citep{perkel:2016} but this will not guarantee reproducibility nor
correctness.
At the educational and methodological levels, things have started to change with a
growing literature on best practices for making computations reproducible
\citep{sandve:2013, crook:2013, wilson:2014, halchenko:2015, janz:2015,
  hinsen:2015}.
  Related initiatives such as Software and Data Carpentry
\citep{wilson:2016} are of note since their goal is {\em to make
scientists more productive, and their work more reliable, by teaching them basic computing skills}.
Such best practices could be applied to already published research codebases as well, provided the original authors are willing to take on the challenge of 
re-implementing their software for the sake of better science.
Unfortunately, this is unlikely since the
incentives for doing such time-consuming work are low or nonexistent.
Furthermore, if the original authors made mistakes in their original
implementation, chances are that they will reproduce their mistakes.\\
% (just an educated guess, we have no data supporting this assertion)
%% At this point, the question is what do we do? Do we have to declare
%% the research to be lost once and for all because the associated software or
%% code is nowhere to be found / lost / damaged / malfunctioning / not runnable /
%% not usable / does not give original results / etc. We would doom ourselves by
%% doing so

@@

The possibility to imply participants beyond the traditional group of
authors, editors, and reviewers is particularly interesting in the
case of ReScience, because it can be helpful to solicit input from the
authors of the original study that is being replicated. For example,
in one recent case
(\href{https://github.com/ReScience/ReScience-submission/pull/28}{\#28}),
a reviewer suggested asking the author of the original work for a
permission to re-use an image. The author intervened in the review and
granted permission.
